### 2022-02-01 paper/slides/covertree/contributions-ancestor.tex
colloquium checkpoint

\uncover<1> {
A \textbf{nearest ancestor cover tree} is a simplified cover tree where every point $p$ satisfies the additional invariant that if $q_1$ is an ancestor of $p$ and $q_2$ is a sibling of $q_1$, then
$$
d(p,q_1) \le d(p,q_2)
$$
}

%\vspace{0.15in}
%Insertion requires rebalancing.
\uncover<2> {
\vspace{-1.1in}
Insertions require rebalancing.

\vspace{0.15in}
No runtime guarantees on the rebalance step.

\vspace{0.15in}
In practice, queries are much faster and construction is only slightly slower.
}
\end{frame}

@@

\begin{frame}[fragile]{Comparing cover trees on \emph{construction} time}
\centering
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/numdist_insert}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
\end{frame}

@@

\begin{frame}[fragile]{Comparing cover trees on \emph{construction and query} time}
\centering
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/numdist}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
\end{frame}

@@

{
\centering
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/protein-simple}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    %\node at (0.6in,0.7in) {\small\rotatebox{90}{ dotted lines: construction only}};
    %\node at (0.75in,0.81in) {\small\rotatebox{90}{ solid lines: construction and query}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
}

>>>>

A \textbf{nearest ancestor cover tree} is a simplified cover tree where every point $p$ satisfies the additional invariant that if $q_1$ is an ancestor of $p$ and $q_2$ is a sibling of $q_1$, then
$$
d(p,q_1) \le d(p,q_2)
$$

@@

\begin{frame}[fragile]{Inserting into a nearest ancestor cover tree}
Inserting into a nearest ancestor cover tree can require rebalancing.
\begin{center}
\begin{tikzpicture}
    [ draw
    , every node/.style={minimum size=10mm,fill=white}
    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-2.3,0) -- (8.6,0)[dotted];
\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];

\uncover<1> {
\node[shape=circle,draw] at (2.5,0) {10}
    child { node[circle,draw] {8}
        child [color=white] {}
        child { node[circle,draw] {11} }
        }
    child [ color=white ] { %node[circle,draw] {12}
        %child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
        %child { node[circle,draw] {13} }
        }
    ;
}

\uncover<2> {
\node[shape=circle,draw] at (2.5,0) {10}
    child { node[circle,draw] {8}
        child [color=white] {}
        child { node[circle,fill=lightred,draw] {11} }
        }
    child  { node[circle,draw] {12}
        %child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
        %child { node[circle,draw] {13} }
        }
    ;
}

\uncover<3> {
\node[shape=circle,draw] at (2.5,0) {10}
    child { node[circle,draw] {8}
        child [color=white] {}
        child [color=white] {}
        }
    child  { node[circle,draw] {12}
        child { node[circle,fill=lightgreen,draw] {11} }
        child [color=white] {}
        %child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
        %child { node[circle,draw] {13} }
        }
    ;
}
\node[fill=none] at (8,3mm) {level 3};
\node[fill=none] at (8,-9mm) {level 2};
\node[fill=none] at (8,-21mm) {level 1};
\end{tikzpicture}
\end{center}

\vspace{0.15in}
No runtime bounds on the rebalancing step.

\vspace{0.15in}
In practice, queries are faster but construction is slower.
\end{frame}

@@

\begin{frame}[fragile]{Comparing cover trees on \emph{construction} time}
\centering
\graphicspath{{covertree/paperimg/}}
\input{covertree/paperimg/numdist_insert}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
\end{frame}

\begin{frame}[fragile]{Comparing cover trees on \emph{construction and query} time}
\centering
\graphicspath{{covertree/paperimg/}}
\input{covertree/paperimg/numdist}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
\end{frame}

@@

{
\centering
\graphicspath{{covertree/paperimg/}}
\input{covertree/paperimg/protein-simple}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    %\node at (0.6in,0.7in) {\small\rotatebox{90}{ dotted lines: construction only}};
    %\node at (0.75in,0.81in) {\small\rotatebox{90}{ solid lines: construction and query}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
}

### 2022-02-01 paper/slides/covertree/experiment-protein.tex
colloquium checkpoint

\begin{frame}[fragile]{The nearest ancestor cover tree}

\definecolor{lightred}{rgb}{1,0.8,0.8}
\definecolor{lightgreen}{rgb}{0.8,1,0.8}
\begin{center}
\begin{tikzpicture}
    [ draw
    , every node/.style={minimum size=10mm,fill=white}
    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-2.3,0) -- (8.6,0)[dotted];
\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
\node[shape=circle,draw] at (0,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw,fill=lightred,line width=1pt] {11} }
        }
    child { node[circle,draw] {12}
        child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
        child { node[circle,draw] {13} }
        }
    ;
\node[shape=circle,draw] at (5,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
        }
    child { node[circle,draw] {12}
        child { node[circle,draw,fill=lightgreen,line width=1pt] {11}  }
        child { node[circle,draw] {13} }
        }
    ;
\node[fill=none] at (8,3mm) {level 3};
\node[fill=none] at (8,-9mm) {level 2};
\node[fill=none] at (8,-21mm) {level 1};
\end{tikzpicture}
\end{center}

\uncover<1> {
A \textbf{nearest ancestor cover tree} is a simplified cover tree where every point $p$ satisfies the additional invariant that if $q_1$ is an ancestor of $p$ and $q_2$ is a sibling of $q_1$, then
$$
d(p,q_1) \le d(p,q_2)
$$
}

%\vspace{0.15in}
%Insertion requires rebalancing.
\uncover<2> {
\vspace{-1.1in}
Insertions require rebalancing.

\vspace{0.15in}
No runtime guarantees on the rebalance step.

\vspace{0.15in}
In practice, queries are much faster and construction is only slightly slower.
}
\end{frame}

@@

\begin{frame}[fragile]{Comparing cover trees on \emph{construction} time}
\centering
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/numdist_insert}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
\end{frame}

\begin{frame}[fragile]{Comparing cover trees on \emph{construction and query} time}
\centering
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/numdist}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
\end{frame}

\begin{frame}[fragile]{All of the cover trees scale similarly}

This experiment uses the protein data and the random walk graph kernel.
\vspace{0.15in}

{
\centering
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/protein-simple}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    %\node at (0.6in,0.7in) {\small\rotatebox{90}{ dotted lines: construction only}};
    %\node at (0.75in,0.81in) {\small\rotatebox{90}{ solid lines: construction and query}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
}

>>>>

@@

\begin{frame}[fragile]{Experiment: protein data bank data}

%This experiment uses the protein data and the random walk graph kernel.
\vspace{0.1in}
Protein distance measured using the random walk graph kernel
\vspace{0.1in}

{
\begin{center}
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/protein-pres}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    %\node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    %\node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    %\node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    %\node at (0.6in,0.7in) {\small\rotatebox{90}{ dotted lines: construction only}};
    %\node at (0.75in,0.81in) {\small\rotatebox{90}{ solid lines: construction and query}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
\end{center}
}

### 2022-02-01 paper/slides/covertree/img-simplifiedcovertree2.tex
colloquium checkpoint

\begin{frame}[fragile]{The nearest ancestor cover tree}

\definecolor{lightred}{rgb}{1,0.8,0.8}
\definecolor{lightgreen}{rgb}{0.8,1,0.8}
\begin{center}
\begin{tikzpicture}
    [ draw
    , every node/.style={minimum size=10mm,fill=white}
    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-2.3,0) -- (8.6,0)[dotted];
\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
\node[shape=circle,draw] at (0,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw,fill=lightred,line width=1pt] {11} }
        }
    child { node[circle,draw] {12}
        child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
        child { node[circle,draw] {13} }
        }
    ;
\node[shape=circle,draw] at (5,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
        }
    child { node[circle,draw] {12}
        child { node[circle,draw,fill=lightgreen,line width=1pt] {11}  }
        child { node[circle,draw] {13} }
        }
    ;
\node[fill=none] at (8,3mm) {level 3};
\node[fill=none] at (8,-9mm) {level 2};
\node[fill=none] at (8,-21mm) {level 1};
\end{tikzpicture}
\end{center}

A \textbf{nearest ancestor cover tree} is a simplified cover tree where every point $p$ satisfies the additional invariant that if $q_1$ is an ancestor of $p$ and $q_2$ is a sibling of $q_1$, then
$$
d(p,q_1) \le d(p,q_2)
$$

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{Inserting into a nearest ancestor cover tree}
Inserting into a nearest ancestor cover tree can require rebalancing.
\begin{center}
\begin{tikzpicture}
    [ draw
    , every node/.style={minimum size=10mm,fill=white}
    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-2.3,0) -- (8.6,0)[dotted];
\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];

\uncover<1> {
\node[shape=circle,draw] at (2.5,0) {10}
    child { node[circle,draw] {8}
        child [color=white] {}
        child { node[circle,draw] {11} }
        }
    child [ color=white ] { %node[circle,draw] {12}
        %child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
        %child { node[circle,draw] {13} }
        }
    ;
}

\uncover<2> {
\node[shape=circle,draw] at (2.5,0) {10}
    child { node[circle,draw] {8}
        child [color=white] {}
        child { node[circle,fill=lightred,draw] {11} }
        }
    child  { node[circle,draw] {12}
        %child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
        %child { node[circle,draw] {13} }
        }
    ;
}

\uncover<3> {
\node[shape=circle,draw] at (2.5,0) {10}
    child { node[circle,draw] {8}
        child [color=white] {}
        child [color=white] {}
        }
    child  { node[circle,draw] {12}
        child { node[circle,fill=lightgreen,draw] {11} }
        child [color=white] {}
        %child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
        %child { node[circle,draw] {13} }
        }
    ;
}
\node[fill=none] at (8,3mm) {level 3};
\node[fill=none] at (8,-9mm) {level 2};
\node[fill=none] at (8,-21mm) {level 1};
\end{tikzpicture}
\end{center}

\vspace{0.15in}
No runtime bounds on the rebalancing step.

\vspace{0.15in}
In practice, queries are faster but construction is slower.
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{Comparing cover trees on \emph{construction} time}
\centering
\graphicspath{{covertree/paperimg/}}
\input{covertree/paperimg/numdist_insert}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{Comparing cover trees on \emph{construction and query} time}
\centering
\graphicspath{{covertree/paperimg/}}
\input{covertree/paperimg/numdist}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    \node at (0.45in,0.6in) {\small\rotatebox{90}{}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{All of the cover trees scale similarly}

This experiment uses the protein data and the random walk graph kernel.
\vspace{0.15in}

{
\centering
\graphicspath{{covertree/paperimg/}}
\input{covertree/paperimg/protein-simple}
\begin{tikzpicture}
    \node[draw,fill=darkred,minimum width=0.03in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.77in) {\small\rotatebox{90}{Original cover tree}};
    \node[draw,fill=darkgreen,minimum width=0.03in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.82in) {\small\rotatebox{90}{Simplified cover tree}};
    \node[draw,fill=blue,minimum width=0.03in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,1.01in) {\small\rotatebox{90}{Nearest ancestor cover tree}};
    \node[minimum width=0.05in,minimum height=0.5in] at (0.45in,0) {};
    %\node at (0.6in,0.7in) {\small\rotatebox{90}{ dotted lines: construction only}};
    %\node at (0.75in,0.81in) {\small\rotatebox{90}{ solid lines: construction and query}};
    \node at (0,-0.5in) {};
\end{tikzpicture}
}

\end{frame}

>>>>

\documentclass[tikz]{standalone}
\begin{document}

\definecolor{lightred}{RGB}{255,200,200}
\definecolor{lightgreen}{RGB}{200,255,200}
\definecolor{lightblue}{RGB}{200,200,255}
\definecolor{darkred}{RGB}{127,0,0}
\definecolor{darkgreen}{RGB}{0,127,0}
\definecolor{darkblue}{RGB}{0,0,127}

\begin{tikzpicture}
    [ draw
    , every node/.style={minimum size=10mm,fill=white}
    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-2.3,0) -- (8.6,0)[dotted];
\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
\node[shape=circle,draw] at (0,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw,fill=lightred,line width=1pt] {11} }
        }
    child { node[circle,draw] {12}
        child { node[circle,draw,fill=lightred,line width=1pt] {9}  }
        child { node[circle,draw] {13} }
        }
    ;
\node[shape=circle,draw] at (5,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
        }
    child { node[circle,draw] {12}
        child { node[circle,draw,fill=lightgreen,line width=1pt] {11}  }
        child { node[circle,draw] {13} }
        }
    ;
\node[fill=none] at (8,3mm) {level 3};
\node[fill=none] at (8,-9mm) {level 2};
\node[fill=none] at (8,-21mm) {level 1};
\end{tikzpicture}
\end{document}

### 2022-02-01 paper/slides/covertree/runtimes-graphs.tex
colloquium checkpoint

\begin{frame}[fragile]{Merging cover trees}

Merging cover trees gives us a parallel tree construction algorithm

\vspace{0.15in}

Sometimes, merging cover trees is \textbf{easy}:

\begin{center}
\begin{tikzpicture}
    [ draw
    , every node/.style={minimum size=10mm,fill=white}
    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-2.3,0) -- (8.6,0)[dotted];
\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
\node[shape=circle,draw] at (0,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw] {9} }
        }
    child [color=white] {}
    %child { node[circle,draw] {12}
        %child { node[circle,draw] {9}  }
        %child { node[circle,draw] {13} }
        %}
    ;
\node[shape=circle,draw,fill=lightgreen] at (5,-12mm) {12}
    %child { node[circle,draw] {8}
        %child { node[circle,draw] {7}  }
        %child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
        %}
    %child { node[circle,draw] {12}
        child { node[circle,draw] {11}  }
        child { node[circle,draw] {13} }
        %}
    ;
\node[fill=none] at (8,3mm) {level 3};
\node[fill=none] at (8,-9mm) {level 2};
\node[fill=none] at (8,-21mm) {level 1};
\end{tikzpicture}
\end{center}

\vspace{0.1in}
No runtime bound on the merge operation, but it is fast in practice

%\vspace{0.1in}
%But, if the runtime is $o(n)$, then we get an algorithm for tree construction that takes time $O(n)$
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{Merging cover trees}

Merging cover trees gives us a parallel tree construction algorithm

\vspace{0.15in}

Sometimes, merging cover trees is \textbf{hard}:

\begin{center}
\begin{tikzpicture}
    [ draw
    , every node/.style={minimum size=10mm,fill=white}
    , level/.style={sibling distance = 23mm/#1, level distance=12mm}
    %,    level distance = 1.5cm}
    , sibling distance=8mm
    ]
\draw (-2.3,0) -- (8.6,0)[dotted];
\draw (-2.3,-12mm) -- (8.6,-12mm)[dotted];
\draw (-2.3,-24mm) -- (8.6,-24mm)[dotted];
\node[shape=circle,draw] at (0,0) {10}
    child { node[circle,draw] {8}
        child { node[circle,draw] {7}  }
        child { node[circle,draw] {9} }
        }
    child [color=white] {}
    %child { node[circle,draw] {12}
        %child { node[circle,draw] {9}  }
        %child { node[circle,draw] {13} }
        %}
    ;
\node[shape=circle,draw,fill=lightred] at (5,-12mm) {11.5}
    %child { node[circle,draw] {8}
        %child { node[circle,draw] {7}  }
        %child { node[circle,draw,fill=lightgreen,line width=1pt] {9} }
        %}
    %child { node[circle,draw] {12}
        child { node[circle,draw] {11}  }
        child { node[circle,draw] {13} }
        %}
    ;
\node[fill=none] at (8,3mm) {level 3};
\node[fill=none] at (8,-9mm) {level 2};
\node[fill=none] at (8,-21mm) {level 1};
\end{tikzpicture}
\end{center}

\vspace{0.1in}
No runtime bound on the merge operation, but it is fast in practice

%\vspace{0.1in}
%But, if the runtime is $o(n)$, then we get an algorithm for tree construction that takes time $O(n)$
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{The effect of parallel tree \emph{construction} on small datasets}
\begin{center}
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/parallel-ancestor-build}
\begin{tikzpicture}
    \node[draw,fill=blue,minimum width=0.05in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,0.63in) {\small\rotatebox{90}{Our cover tree}};
    \node[minimum width=0.05in,minimum height=0.3in] at (0.45in,0) {};
    \node at (0.45in,0.61in) {\small\rotatebox{90}{}};
    \node at (0,-0.475in) {};
\end{tikzpicture}
\end{center}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{Parallel tree construction really matters on larger data sets}

%on small datasets with cheap metrics, parallel construction is less useful

\vspace{0.1in}
On large datasets with an expensive metric, parallelism is more useful

\vspace{0.15in}
Yahoo! Flickr dataset with 1.5 million images and earth mover distance

%\vspace{0.2in}
\vspace{0.15in}
\begin{center}
\Large
\begin{tabular}{ccccc}
\hline
num cores
 & \multicolumn{2}{c}{simplified tree} & \multicolumn{2}{c}{nearest ancestor tree} \\
%& \multicolumn{2}{c}{construction} & \multicolumn{2}{c}{construction} \\ %\cline{2-5}
& time & speedup & time & speedup \\
\hline
\hline
1  & 70.7 min & 1.0 & 210.9 min& 1.0\\
2  & 36.6 min & 1.9 & 94.2 min & 2.2\\
4  & 18.5 min & 3.8 & 48.5 min & 4.3\\
8  & 10.2 min & 6.9 & 25.3 min & 8.3\\
16 & 6.7 min & 10.5 & 12.0 min & 17.6\\
\hline
\end{tabular}
\end{center}

\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{frame}[fragile]{The effect of parallel tree \emph{construction and query}}
\begin{center}
\graphicspath{{slides/covertree/paperimg/}}
\input{slides/covertree/paperimg/parallel}
\definecolor{colorOrig}{RGB}{102,51,0}
\definecolor{colorMlpack}{RGB}{204,153,0}
\begin{tikzpicture}
    \node[draw,fill=colorOrig,minimum width=0.05in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.79in) {\small\rotatebox{90}{Reference cover tree}};
    \node[draw,fill=colorMlpack,minimum width=0.05in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.80in) {\small\rotatebox{90}{MLPack's cover tree}};
    \node[draw,fill=blue,minimum width=0.05in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,0.63in) {\small\rotatebox{90}{Our cover tree}};
    \node[minimum width=0.05in,minimum height=0.3in] at (0.45in,0) {};
    \node at (0.45in,0.61in) {\small\rotatebox{90}{}};
    \node at (0,-0.475in) {};
\end{tikzpicture}
\end{center}

>>>>

\begin{frame}[fragile]{Cover tree performance comparisons}
\begin{center}
\graphicspath{{covertree/paperimg/}}
\input{slides/covertree/paperimg/parallel}
\definecolor{colorOrig}{RGB}{102,51,0}
\definecolor{colorMlpack}{RGB}{204,153,0}
\begin{tikzpicture}
    \node[draw,fill=colorOrig,minimum width=0.05in,minimum height=0.3in] at (0,0) {};
    \node at (0,0.79in) {\small\rotatebox{90}{Reference cover tree}};
    \node[draw,fill=colorMlpack,minimum width=0.05in,minimum height=0.3in] at (0.15in,0) {};
    \node at (0.15in,0.80in) {\small\rotatebox{90}{MLPack's cover tree}};
    \node[draw,fill=blue,minimum width=0.05in,minimum height=0.3in] at (0.3in,0) {};
    \node at (0.3in,0.63in) {\small\rotatebox{90}{Our cover tree}};
    \node[minimum width=0.05in,minimum height=0.3in] at (0.45in,0) {};
    \node at (0.45in,0.61in) {\small\rotatebox{90}{}};
    \node at (0,-0.475in) {};
\end{tikzpicture}
\end{center}

@@
